---
title: "p8105_hw1_raj2152"
author: "Rachelle Juan"
date: "9/26/2021"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

## Problem 1

First, create a data frame and show resulting output table.

```{r}
set.seed(1)

df = tibble(
  rand_sample = rnorm(10),
  logical_vec = rand_sample > 0,
  char_vec = vector("character", 10),
  factor_vec = factor(x = character(10),3)
)

df
```

Try to take the mean of each variable in the data frame, after pulling each one:
```{r}
mean(pull(df,rand_sample))
mean(pull(df,logical_vec))
mean(pull(df,char_vec))
mean(pull(df,factor_vec))
```

I could only get the mean for rand_sample and the logical_vec variables. The character and factor variables returned 'NA' and gave a warning that the argument is not numeric or logical. 

Attempt to convert variable types to numeric.

```{r, eval = FALSE}
as.numeric(pull(df,logical_vec))
as.numeric(pull(df,char_vec))
as.numeric(pull(df,factor_vec))
```

The logical variable converts to numeric boolean values (1 if True, 0 if false) and the character and factor variables convert to 'NA' values. This explains why we're able to get a mean for logical but not character and factor variables.

## Problem 2

Load the penguins dataset and get important information, such as variable names, size of data set, and mean flipper length:
```{r}
data("penguins", package = "palmerpenguins")

names(penguins)
nrow(penguins)
ncol(penguins)
skimr::skim(penguins)
```


